\subsection{Fit demonstration for contributions of $I=0$, $I=1$, and their interference term}
\input{discussion/spectra/figs/fit_A_scale}

First, free parameterize the strength of the second scattering of isospin $I=0,1$ as $\Tmat'^{I=0, 1} = A_{I=0,1}\Tmat^{I=0,1}$, where $A_{I=0,1}$ is the free parameters.

Here, the scattering strength of $I=1,0$ and its interference term are expressed as
\begin{align}
  & f_{I=0}(m_{\pi\Sigma})=\left| \Cfirst^0 \Tmat^{I=0} \right|^2 \\
  & f_{I=1}(m_{\pi\Sigma})=\left| \Cfirst^1 \Tmat^{I=1} \right|^2 \\
  & f_{int}(m_{\pi\Sigma})=2\mbox{Re}( \Cfirst^0 \Cfirst^1 \Tmat^{I=0} \Tmat^{I=1} ) \label{eq:interfer}
\end{align}

Eq.(\ref{eq:Charge_piS}, \ref{eq:pimS0}) can be expressed as

\begin{align}
  \frac{d\sigma}{d\Omega dM}(\pi^\mp \Sigma^\pm) = & A_{I=0} f_{I=0}(m_{\pi\Sigma}) + A_{I=1} f_{I=1}(m_{\pi\Sigma}) \nonumber \\
                                                   & + \sqrt{A_{I=0}A_{I=1}} f_{int}(m_{\pi\Sigma}) \label{eq:scale_Charge} \\
  \frac{d\sigma}{d\Omega dM}(\pi^- \Sigma^0) = & A_{I=1} f_{I=1}(m_{\pi\Sigma}) \label{eq:scale_pimS0} 
\end{align}

\input{discussion/fit_param}
The results of fitting our spectra by varying the model.A by parameterization according to Eq.(\ref{eq:scale_Charge}-\ref{eq:scale_pimS0}) are shown in Fig.\ref{fig:fit_A_scale}.
where $A_{I=0}$ is $\fitAscaleIz$ and $A_{I=1}$ is $\fitAscaleIo$.
$I=0$ suppresses the overall strength due to the long tail below the $\bar{K}N$ threshold, but still does not explain the overall spectral shape.
The strength at $I=1$ remains almost unchanged, while the strength at $I=0$ is suppressed by the long tail below the $\bar{K}N$ threshold.
Therefore, the strength of the interference term is also smaller and deviates from the experimental value.
The $\chi^2/NDF$ for this fit is $\fitAscaleChi = \fitAscaleChiNum$.

\input{discussion/spectra/figs/fit_B_scale}

\input{discussion/spectra/figs/fit_B_phase_fixI1}

\input{discussion/spectra/figs/fit_B_phase}

The results of the fit using Model.B are shown in Figure.\ref{fig:fit_B_scale}.
The parameters in this fit are $A_{I=0}=\fitBscaleIz$ and $A_{I=1}=\fitBscaleIo$.
And, the $\chi^2/NDF$ of this fit is $\fitBscaleChi = \fitBscaleChiNum$, which explains our spectra better than the model.A.
In this fit, the theoretical value of $I=1$ is stronger and the strength of $I=0$ is weaker.
Since each value is constrained by the interference term, each spectrum appears to be inadequate in the region above the $\bar{K}N$ threshold.
Therefore, we introduce a parameter, $A_{int}$, which allows us to move the interference term independently, as follows.

\begin{align}
  \frac{d\sigma}{d\Omega dM}(\pi^\mp \Sigma^\pm) = & A_{I=0} f_{I=0}(m_{\pi\Sigma}) + A_{I=1} f_{I=1}(m_{\pi\Sigma}) \nonumber \\
  & + \sqrt{A_{I=0}A_{I=1}} A_{int} f_{int}(m_{\pi\Sigma}) \label{eq:scale_Charge_2} \\
  \frac{d\sigma}{d\Omega dM}(\pi^- \Sigma^0) = & A_{I=1} f_{I=1}(m_{\pi\Sigma}) \label{eq:scale_pimS0_2} 
\end{align}

We first consider physical mean of the $A_{int}$ parameter.
The interference terms are expressed as in Eq(\ref{eq:interfer}).
The phase difference between the terms for each isospin, $\Cfirst^{I=0,1} \Tmat^{I=0,1}$ write $\delta \theta$ and the equation can be rewrite as follow.

\begin{equation}
  f_{int}(m_{\pi\Sigma})=2\left| \Cfirst^0 \Cfirst^1 \Tmat^{I=0} \Tmat^{I=1} \right| \cos \delta \theta \label{eq:interfer}
\end{equation}

In general, the phase of the scattering amplitude depends on the total energy, but in the first step of $K^-p \rightarrow \bar{K}N$ scattering,
the total energy is determined by the $^K-$ beam and is independent of the $\pi \Sigma$ mass, which is considered reasonable.
Moving the interference terms independently is equivalent to adding to this phase difference a constant parameter independent of the $\pi \Sigma$ mass.

This parameter, which moves the interference terms independently, only affects the $\pi^-\Sigma^+$ and $\pi^+\Sigma^-$ modes,
while the $\pi^-\Sigma^0$ mode is determined only by the $I=1$ strength.
Therefore, we obtained the strength of $I=1$ from the $\pi^- \Sigma^0$ spectrum in the first step
and the strength of $I=0$ and the parameter about the interference term  by the fitting of the $\pi^- \Sigma^+$ and the $\pi^+ \Sigma^-$ spectra in the next step.
As a result, the spectra is obtained as shown in Fig.\ref{fig:fit_B_phase_fixI1} and each parameter is obtained as $A_{I=0}=\fitBBIz$, $A_{I=1}=\fitBBIo$, and $A_{int}=\fitBBphase$.
Evaluating this fitting with equal weights for all spectra as before the introduction of the interference term gives $\chi^2/NDF$ as $\fitBBChi = \fitBBChiNum$,
which is an improvement over before the interference term is introduced.

We also performed simultaneous fitting of all these parameters in all spectra.
The $\chi^2/NDF$ of this fit is $\fitBChi = \fitBChiNum$, which is almost the same value as when the strength of $I=1$ is fixed.
As a result, the spectra is obtained as shown in Fig.\ref{fig:fit_B_phase} and each parameter is obtained as $A_{I=0}=\fitBIz$, $A_{I=1}=\fitBIo$, and $A_{int}=\fitBphase$.
% To do  %% 
The values of these parameters are very close to those of the case with fixed the strength of $I=1$, and these differences may be considered as systematic errors.
Therefore, these parameters are estimated to $A_{I=0}=0.684 \pm 0.002\mbox{(Systematic)} \pm 0.017\mbox{(fitting)}$,
$A_{I=1}=1.516 \pm 0.054 \mbox{(Systematic)} ^{+0.058} _{-0.059} \mbox{(fitting)}$, and
$A_{int}=0.820 \pm 0.09 \mbox{(Systematic)} \pm 0.03 \mbox{(fitting)}$.
That implies adding a constant offset of $34.9 \pm 0.9 \mbox{(Systematic)} \pm 0.3 \mbox{(fitting)}$ degrees the phase difference between $I=0$ and $I=1$.

%% \begin{table}
%%   \begin{tabular}{c|c|c|c}
%%     Scale      & $\fitBscaleIz$ & $\fitBscaleIo$ & - \\
%%     Fix $I=1$  & $\fitBBIz$ & $\fitBBIo$ & $\fitBBphase$ \\
%%     Phase      & $\fitBIz$ & $\fitBIo$ & $\fitBphase$ \\
%%   \end{tabular}
%% \end{table}
