
\chapter*{\centering \begin{normalsize}Abstract\end{normalsize}}
\thispagestyle{empty}
%\addcontentsline{toc}{chapter}{Abstract}
%\begin{quotation}
%\begin{abstract}
%\noindent % abstract text
We have carried out the first stage physics run of the J-PARC E15 experiment to search for the $K^-pp$ bound state in the $^3$He($K^-,n$) reaction at the kaon beam momentum of 1 GeV/$c$. The experiment was performed in May, 2013 at the K1.8BR beam line in the J-PARC hadron experimental facility, Tokai, Japan. Approximately 5.2 $\times 10^{9}$ kaons bombarded on a helium-3 target during the data taking period of about 4 days. 

The newly constructed spectrometer system at the K1.8BR experimental area consists of a beam line spectrometer, a liquid helium cryogenic target, a cylindrical detector system (CDS) which surrounds the target, and a neutron detection system at the forward angle. The spectrometer system achieved design performance, and a $^3$He($K^-,n)X$ missing-mass resolution is evaluated to be $\sim$10 MeV/$c^2$ ($\sigma$) in the region of interest.

A neutron missing-mass distribution is obtained under a semi-inclusive condition by requesting at least 1 charged particle reconstructed by the CDS whose acceptance is from 54 to 126 degrees in the polar angle. The spectrum is almost free from accidental backgrounds, and shows a clear peak structure mainly composed of the quasi-free $K^-$ elastic reaction and the charge-exchange $K^0_s$ production. We observe a tail structure just below the $K^-pp$ binding threshold, which cannot be explained by experimental effects, such as detector resolution and unphysical backgrounds, nor known elementally processes. The number of such unknown excess is evaluated to be 1462 $\pm$ 58(stat.) $\pm$ 122(syst.) events in the missing-mass region from 2.29 to 2.37 GeV/$c^2$, while the background is to be 568 $\pm$ 57(stat.) $\pm$ 121(syst.) events. Thus the observed excess is statistically significant. This is the first observation of a significant structure just below the $K^-pp$ threshold,   which is a possible candidate of $S=-1$ di-baryon states such as the theoretically predicted $K^-pp$ bound state. 
As the possible sources of the unknown excess, formation of the $K^-pp$ bound state and the $\Lambda(1405)n$ branch of non-mesonic two-nucleon absorption processes are discussed. In addition, upper limits of the formation cross section of the deeply-bound $K^-pp$ state in the $^3$He($K^-,n$) reaction are determined for the deep binding region energies of larger than 90 MeV. They are obtained to be 0.02$\sim$0.4 mb/sr at $\theta_{lab}=0^\circ$ at a 95\% confidence level, for the widths of 20, 60, and 100 MeV/$c^2$ with a decay mode of $K^-pp\to \Lambda p$. 
%\end{abstract}
%\end{quotation}
%\clearpage

