\chapter{$K^0$ 2-step and Direct-$\Lambda(1520)$ production}
\section{Template fitting}
\input{discussion/template_fitting/figs/fit_nK0_IM}
In quasi-elastic scattering, the momentum of the spectator is small due to the Fermi motion of the spectator.
Therefore, the scattered $K^0 n$ has almost all the energy, so the invariant mass is distributed around the kinematic threshold.

However, our experimental data, represented by the error bars in Fig.\ref{fig:fit_nK0_IM}, have widely distributed components.
The spectra reproduced in the MC simulations are also plotted as coloured lines in the same figure.
The bold line shows the actual K0-produced signal, while the green line indicates 1-step quasi-elastic scattering.
The two other dark red and dark blue lines indicate 2-step and direct $\Lambda(1520)$ production, which will be discussed in more detail below.
The thin coloured lines represent the background,
with red, blue, purple and orange indicating backward $\pi^- \Sigma^+$, backward $\pi^+ \Sigma^-$, $\Sigma^-_{forward}$ and $\Sigma^+_{forward}$, respectively.

In the 2-step $K^0$ reaction, the recoiled $K^0$ scatters with residual nucleons and shares its energy with them.
Therefore, the invariant mass of n K0 is widely distributed in the allowed kinematic region.
A bump structure is observed near $\Lambda(1520)$, indicating that $K^- d \rightarrow n \Lambda(1520)$ reaction and $\Lambda(1520)\rightarrow n K^0 $decay are taking place.
As a result of this template fit, the $-2\log \Lambda$ is estimates as $\KzeroFitChi$ and $NDF$ is $\KzeroFitNDF$, so $-2\log \Lambda/NDF \sim \KzeroFitChiNDF$.
The, the ratio of 1-step to true $K^0$ production excluding background is estimated to $\KzeroOneStepRatio$, 2-step $\KzeroTwoStepRatio$ and direct-$\Lambda(1520)$ $\KzeroLsRatio$.

\section{Affect to the $d(K^-, n)$ Spectra}
\input{discussion/template_fitting/figs/KN_MM_K0}
We explain effect of these reactions contaminating into the main signal, $d(K^-, n)"\pi^{\mp}\Sigma^{\pm}"$, as background.
Fig.\ref{fig:KN_MM_K0} shows the $d(K^-, n)$ missing mass with $K^0$ identified.
The data is represented by error bars with the MC where the K0 was actually created by a bold line and the background by a thin line.
Since the spectral shape of $d(K^-,n)$ is determined by the initial $\bar{K}N$ scattering, the 2-step reaction is almost identical to the 1-step reaction.
On the other hand, the direct $\Lambda(1520)$ production makes a bump structure on $d(K^-, n)$ too.
Since the contribution of this reaction is so small, this background effect is almost no change.

\section{Conversion to the Cross Section}
\input{discussion/conversion/figs/K0_cos_mom}
\input{discussion/conversion/figs/K0_spec}

For $K^0$ production events, we use acceptance for $K^0$ kinematics because all detected particles are of $K^0$ origin.
We estimate the two-dimensional acceptances for $K^0$ momentum and $K^0$ scattering angles as shown in Fig\ref{fig.K0_cos_mom_acc}, and weight each event to correct for acceptances.
Fig.\ref{fig:K0_spec} shows acceptance corrected spectra of $K^0$ production with reproduced BG by MC simulations.
It can be seen that the data are concentrated in the backward and high momentum regions where the acceptances are small,
while the MC is distributed over the whole region as shown in Fig.\ref{fig:K0_cos_mom}.
In other words, the acceptance correction suppresses BG and emphasizes true $K^0$ production.

Multiplying the obtained spectra by the conversion factor discribed in Sectrion.\ref{sec:conversion_factor} yields the cross sections shown in Fig.\ref{fig:nK0_CS}.
The $d(K^-,n)"nK^0"$ spectra do not contain information below the $\bar{K}N$ threshold but are suitable for studying the $d(K^-, n)$ reaction.
This spectrum is similar to the bump structure of the so-called quasi-elastic scattering.
This spectrum contains about 12\% of the 2-step reaction described in the previous section.
Since the missing mass of $d(K^-,n)$ is determined by the $K^- N \rightarrow \bar{K}N$ scattering of the first reaction, this spectrum has almost the same shape as quasi-elastic scattering.
The strength of the 2-step at the quasi-elastic scattering bump is $35 mb/\Omega \cdot \mbox{MeV}$, which is consistent with $d(K^-, N)"\pi \Sigma"$ in order.

\input{discussion/conversion/figs/K0_CS}
