Here, the spectra are decomposed into the $I=0$, $I=1$, and interference components in order to clarify the contriutions of these factors.
The obtained spectrum can be expressed as follows from the isospin relation.

\newcommand{\Tmat}{T_{\bar{K}N \rightarrow \pi \Sigma}}
\newcommand{\Cfirst}{C_{K^- N \rightarrow \bar{K}N}}
\newcommand{\CS}{\frac{d\sigma}{d\Omega dM}}
\begin{align}
  \CS(\pi^\mp \Sigma^\pm) \propto & \left| \Cfirst^0 \Tmat^{I=0} \mp \Cfirst^1 \Tmat^{I=1} \right|^2 \nonumber \\
  = & \left| \Cfirst^0 \Tmat^{I=0} \right|^2 + \left| \Cfirst^1 \Tmat^{I=1} \right|^2 \nonumber \\
    & \mp 2\mbox{Re}( \Cfirst^0 \Cfirst^1 \Tmat^{I=0} \Tmat^{I=1} ) & \label{eq:Charge_piS} \\
  \CS(\pi^- \Sigma^0) \propto & \left| \Cfirst^1 \Tmat^{I=1} \right|^2 \label{eq:pimS0}
\end{align}

Here, $\Tmat^{I=0,1}$ represents the $T$ matrix of the second $\bar{K}N \rightarrow \pi \Sigma$ scattering for isospin $I=0$ and $I=1$.
Additionally, $\Cfirst^{0,1}$ denotes the factor for the first $K^- p \rightarrow \bar{K}N$ scattering,
corresponding to the isospin $I=0$ and $I=1$ components of the second scattering.

Since it can be expressed as shown in Equation (\ref{eq:Charge_piS}), (\ref{eq:pimS0}),
the spectra corresponding to $I=0$, $I=1$, and their interference terms can be written as follows.
\begin{align}
   \CS(I=0) \propto & \frac{1}{2}\left( \CS(\pi^- \Sigma^+)+\CS(\pi^+ \Sigma^-)-\CS(\pi^-\Sigma^0) \right) \nonumber \\
            = & \left| \Cfirst^0 \Tmat^{I=0} \right|^2 \label{eq:I0}\\
   \CS(I=1) \propto & \CS(\pi^- \Sigma^0) \nonumber \\
            = & \left| \Cfirst^1 \Tmat^{I=1} \right|^2 \label{eq:I1}\\
   \CS(int) \propto & \left( \CS(\pi^- \Sigma^+)-\CS(\pi^+\Sigma^+) \right) \nonumber \\
            = & 4\mbox{Re}( \Cfirst^0 \Cfirst^2 \Tmat^{I=0} \Tmat^{I=1} ) \label{eq:interfer}
\end{align}

The spectrum is transformed according to this formula.
We introduce scaling parameters $S_{I=0}$ and $S_{I=1}$ to adjust the intensities of the $I=0$ and $I=1$ components,
respectively, so that the overall spectral shape becomes more comparable to the theoretical spectrum.
The interference terms are scaled by $\sqrt{S_{I=0}S_{I=1}}$, as described in Equation \ref{eq:interfer}.

\input{discussion/spectra/figs/fit_scale}
\input{discussion/spectra/table/DCC_poles}

By fitting with these parameters, we obtain $S_{I=0} = \fitAscaleIz$ and $S_{I=1} = \fitAscaleIo$ for Model A,
and $S_{I=0} = \fitBscaleIz$ and $S_{I=1} = \fitBscaleIo$ for Model B.
The results of these fits are shown in the Fig.\ref{fig:fit_scale} : the left panel corresponds to Model A, and the right panel to Model B.
The top subpanels show the spectra for the $I=0$ component, the middle ones for the $I=1$ component (i.e., the $\pi^-\Sigma^0$ spectrum),
and the bottom ones for the interference term.

In Model B (right panel), a reasonably good agreement is observed across all spectra.
In contrast, Model A (left panel) reproduces the central $I=1$ term well, but the upper $I=0$ and lower interference terms
appear to be underestimated in the fit results in the quasi-elastic scattering region.
Indeed, the $\chi^2/NDF$ values are $\fitBscaleChi = \fitBscaleChiNum$ for Model B and
$\fitAscaleChi = \fitAscaleChiNum$ for Model A, indicating a significantly better fit for Model B.
This discrepancy is considered to arise from the fact that the theoretical spectrum for $I=0$ possesses a long-tailed component in the bound region.
Table \ref{table:DCC_poles} summarizes the parameters of the $I=0$ pole used in the theoretical calculations for the fit.
This is attributed to the large imaginary part of pole 1,
which is strongly coupled to the $\bar{K}N$ channel and therefore has a pronounced effect in this experiment.

As shown in Eq.(\ref{eq:interfer}), the phase difference between $I=0$ and $I=1$ modifies the interference term.
We demonstrate that introducing this phase difference as a fitting parameter leads to an improved fit.
The following discussion focuses exclusively on Model B, which provided the better overall agreement.
Since the $I=1$ component is determined solely from the experimental spectrum, two fitting strategies can be considered
(i) first fixing the $I=1$ contribution by $\pi^- \Sigma^0$ spectrum, or (ii) fitting all spectra simultaneously.
The results obtained from these two approaches are presented in Fig. \ref{fig:fit_B_phase_fixI1} and \ref{fig:fit_B_phase}.



\input{discussion/spectra/figs/fit_B_phase_fixI1}
\input{discussion/spectra/figs/fit_B_phase}

