\section{Demonstration of fitting by DCC models}

\input{discussion/fit_param}

Next, we performed demonstration of fitting by DCC models to discuss each component how to contribute each spectra.
First, we use the strength of $I=0$ and $I=1$ as free parameter, which scale $I=0$ and $I=1$ spectra.
The interferance term also change corespond to the isospin relation  as follow rrepresentation.

\input{discussion/eq/CS_isospin_scale}

Where, $A_{I=0}$ and $A_{I=1}$ is scaling factor introduced as 2-step scattering strength.
And interference term is changed according to square root of each strength.

Fig.[\ref{fig:fit_A_scale}] shows about fitting result of Model.A,
in which above figures show obtained spectra and bottom figures show calculated spectra.
We note that fitting are used only above 3 spectra.
At the result, we obtain $A_{I=0}=\fitAscaleIz$ and $A_{I=1}=\fitAscaleIo$ with $\chi^2/NDF=\fitAscaleChi \sim \fitAscaleChiNum$.
In the model.A, $\pi^-\Sigma^0$ of $I=1$ is obtained good matched, that strongly affect above the threshold, but I=0 below the threshold is not matched.
Therefore, the model.A can not explained obtained spectra, as the  shown Fig.[\ref{fig:fit_A_scale}].

\input{discussion/figs/fit_A_scale}
\input{discussion/figs/fit_B_scale}

\input{discussion/figs/fit_B_fix_phase}
\input{discussion/figs/fit_B}

On the other hand, the result of the model.B is shown as the Fig.[\ref{fig:fit_B_scale}], and the parameters are obtained at
$A_{I=0}=\fitBscaleIz$ and $A_{I=1}=\fitBscaleIo$ with $\chi^2/NDF=\fitBscaleChi \sim \fitBscaleChiNum$.
In the model.B,	$I=1$ strength is recovered and	overall	each spectra shape are matched.
But, theoretical strength of $\pi^+\Sigma^-$ is shortage above the $\bar{K}N$ threshold.
That appears in $I=0$ spectra.

Next, we introduce scaling factor $B$ about interference term  to study how to improve fitting and how interference term work.
Then, \pimSp and \pipSm cross section represents as follow.
\input{discussion/eq/CS_isospin_scale_B}

Because $\pi^-\Sigma^0$ is pure $I=1$ channel, we performed fitting $I=1$ channel is determined from only $\pi^-\Sigma^0$, then $I=0$ and the interference term decided,
whose result is shown in Fig.[\ref{fig:fit_B_fix_phase}].
The $\chi^2/NDF=\fitBBChi \sim \fitBBChiNum$ is improved than $\fitBscaleChiNum$ of Fig.[\ref{fig:fit_B_scale}]. 
Parameters are $A_{I=0}=\fitBBIz$, $A_{I=1}=\fitBBIo$ and $B=\fitBBphase$ in this fitting.

The case of simultaneous fitting of these three parameters is shown in the Fig.[\ref{fig:fit_B}],
whose $\chi^2/NDF=\fitBChi \sim \fitBChiNum$ is almost same at $\fitBBChiNum$ of the case of $I=1$ separately decided.
Then, parameters is $A_{I=0}=\fitBIz$, $A_{I=1}=\fitBIo$ and $B=\fitBphase$.

Table.[\ref{table:fit}] lists fit parameters using the DCC model.
$I=0$ component is scaled down to $72\%$ and $I=1$ component is scaled up to $142\%$ at fitting using $I=0$ and $I=1$  scale factor.
Then the interference factor is added, the factor of $I=0$ component is a bit descried and become to $68\%$, and
the factor of $I=1$ component is increased and change to $146-156\%$.
The interference term is descried to $83-81\%$.

% \input{discussion/fit_table}
