\subsection{Acceptance correction} 

\input{discussion/conversion/figs/kn_acc}
\input{discussion/conversion/figs/kp_acc}

The acceptance of $d(K^-,n)"\pi^{\mp}\Sigma^{\pm}"$ and $d(K^-,p)"\pi^-\Sigma^0$ is corrected by MC simulations
in which nucleons are injected at a forward angle into the covered region of a forward detector with a uniform $\pi\Sigma$ mass distribution.
Since the solid angle of the forward detector is evaluated as subsection.\ref{subsec.XXX}, we adapt as the denominator the events for which the forward detector is analyzable.
The same analysis procedure as for the real data is applied to the MC simulation, and the final survival rate is evaluated and used as the acceptance.
That is, for $d(K^-, n)"\pi^{\mp}\Sigma^{\pm}"$, we apply $d(K^-, n \pi^+ \pi^-)"n"$ final state selection and rejection of $K^0$ and $\Sigma_{forward}$.
For $d(K^-, p)"\pi^-\Sigma^0"$, we apply the $d(K^-, p \pi^- \pi^-)"p \gamma"$ and $d(K^-, p \pi^-)"\Sigma^0"$ selections.
Fig.\ref{fig:kn_acc} shows the acceptance of $d(K^-, n)\pi^{\mp} \Sigma^{\pm}$.
Dents above the $\bar{K}N$ threshold are due to $K^0$ rejection.
The difference in absolute values between $\pi^- \Sigma^+$ and $\pi^+ \Sigma^-$ is due to the branching ratio of the $\Sigma$ decay.
Fig.\ref{fig:kp_acc} shows the acceptance of $d(K^-, p)"\pi^-\Sigma^0"$.

\input{discussion/conversion/figs/K0_cos_mom}
\input{discussion/conversion/figs/K0_spec}

For $K^0$ production events, we use acceptance for $K^0$ kinematics because all detected particles are of $K^0$ origin.
We estimate the two-dimensional acceptances for $K^0$ momentum and $K^0$ scattering angles as shown in Fig\ref{fig.K0_cos_mom_acc}, and weight each event to correct for acceptances.
Fig.\ref{fig:K0_spec} shows acceptance corrected spectra of $K^0$ production with reproduced BG by MC simulations.
It can be seen that the data are concentrated in the backward and high momentum regions where the acceptances are small,
while the MC is distributed over the whole region as shown in Fig.\ref{fig:K0_cos_mom}.
In other words, the acceptance correction suppresses BG and emphasizes true $K^0$ production.
