\subsection{Conversion spectra to the cross section}

\input{discussion/conversion/figs/spectra}
\input{discussion/conversion/table/KN_scaling}
\input{discussion/conversion/table/KP_scaling}

The obtained spectra are converted to cross sections.
For this purpose, the target, beam, and DAQ efficiencies are summarized as luminosity.
The target and beam quantities are discussed in Sections.\ref{sec:target} and \ref{sec:Kbeam}, respectively.
The DAQ efficiency consists of two parts, one of which is the DAQ live rate and the other is the trigger efficiency, described in Sections.\ref{sec:DAQ_live_rate} and \ref{sec:trigger}.
Detector efficiency is also evaluated and corrected for conversion to cross sections.
The CDC, NC, and PC efficiencies are described in Sections.\ref{sec:CDC}, \ref{sec:NC}, and \ref{sec:PC}, respectively. 
These conversion factors are common for the $\pi \Sigma$ spectra.
These factors are summarized in Table.\ref{table:KN_scaling} and Table.\ref{table:KP_scaling} about $d(K^-, n)$ and $d(K^-, p)$, respectively.

On the other hand, the acceptances depend on the $\pi \Sigma$ mass spectra.
In the case of $d(K^-, n)"\pi^{\mp} \Sigma^{\pm}"$, the separation ratio of $\pi^- \Sigma^+$ and $\pi^+ \Sigma^-$ is also depend on.
We obtain the cross section of $d(K^-, n)"n K^0"$, $d(K-, n)"\pi^-\Sigma^0"$ and $d(K^-, p)"\pi^- \Sigma^0"$ by adapting the these corrections,
which are shown in Figure.\ref{fig:nK0_CS}, Figure.\ref{fig:ChargeCS}, and Figure.\ref{fig:pimS0_CS}, respectively.

% We discuss the physical mean about obtained spectra.
