\subsection{Cylindrical detector hodoscope}
The CDH is a segmented plastic scintillation counter used for the charged particle trigger and particle identification.
The CDH is located at a radius of 544mm from the beam axis covering a polar angle range from 54 to 126 degree corresponding to a solid angle coverage of 59$\%$ of 4$\pi$.

The CDH consists of 36 modules, individually mounted on the inner wall of the solenoid magnet.
The scintillators are mode of ELJEN EJ-200, with dimensions of 790mm in length, 99mm in width, and 30mm in thickness.
The scintillation light is transferred through light guides to a pair of Hamamatsu R7761 fine-mesh 19-dynode photomultipliers 1.5 inches in diameter.

The CDH is operated in the 0.7T magnetic field with a typical PMT gain of $\sim 10^6$.
The measured average time resolution of the CDH without a magnetic field is $71\pm3$ ps ($\sigma$), obtained with cosmic ray data. The error represents the variation among the segments.

\subsection{Inner hodoscope}
An inner hodoscope (IH) is a segmented plastic scintillation counter mounted on the inner wall of the CFRP cylinder of the CDC at a radius of 140mm from the beam axis.
The IH consists of 24 ELJEN EJ-200 scintillators with a dimension of 600mm in length, 27mm in width, and 3mm in thickness.
Each segment is overlapped by 1mm due to the strong magnetic field and limited space, multi-pixel photon counters (MPPCs) with a 3mm $\times$ 3mm sensitive area were used (Hamamatsu S10362-33-100C).
The scintillation light is collected by 4 wavelength-shifting fibers embedded in the scintillator and connected to an MPPC with a specially designed connector.
The MPPC signal is read out by using a preamplifirer.

The IH was used as a trigger counter for the efficiency estimation of the CDC.
The IH was removed in MR RUN78 to increase acceptance for the backward scattered proton.



