\input{intro/figs/KN_int}

Considering the $\Lambda(1405)$ as a $\bar{K}N$ bound state, the $\bar{K}N$ interaction is expected to be attractive.
From the 1960's to the 1980's, various $K^-p \rightarrow$ meson-baryon, e.g., $K^- p$, $K^0 n$, $\pi \Lambda$, $\pi \Sigma$, and so on,
scattering data were measured on a hydrogen target using bubble chambers to study the $\bar{K}N$ interaction \cite{CERN1,CERN2,CERN3,CERN4,Gopal}.
This method of course did not allow access below the $\bar{K}N$ mass threshold and measurements in the low momentum region were difficult and data were insufficient.
Nevertheless,
the value of the $\bar{K}N$ interaction at the $\bar{K}N$ mass threshold was obtained by extrapolating it from the high momentum region,
where abundant data exist, using several models \cite{KN_int_1, KN_int_2, Martin, KN_int_3}.
These values are shown in Figure \ref{fig:KN_int} as the characteristic X-ray values for kaonic hydrogen, discussed below.
Due to the lack of data in the low momentum region, these values varied.
However, they were all attractive and consistent with the $\Lambda(1405)$ being a $\bar{K}N$ bound state.

An attempt to measure $\bar{K}N$ interactions at the $\bar{K}N$ mass threshold using kaonic hydrogen has been proposed.
In this method, a $K^-$ meson beam is stopped in a hydrogen target,
and the characteristic $X$-rays emitted when the kaon binds to a proton are utilized.
In the case of nucleon-meson, the characteristic $X$-ray is affected not only by electromagnetic interactions but also by the strong interactions
i.e. $\bar{K}N$ interaction,
leading to a shift in energy and a gain in width compared to the case where only electromagnetic interactions are present.
According to Deser-Trueman formula \cite{Deser, Deser2}, these shift and width are model-independent and given by
$\Delta E^{s}_{1}-\frac{i}{2}\Gamma_{1}=-2\alpha^3\mu_{c}^2a_{K^-p}$.
Where $\alpha$ is the fine structure constant, $\mu_{c}$ is the mass of the $K^-$-$p$ system,
and $a_{K^-p}$ is the scattering length of the $\bar{K}N$ interaction.
Several attempts were made in the 1980s using liquid hydrogen targets \cite{KaonicH_1, KaonicH_2, KaonicH_3}.,
but the results showed a positive energy shift, indicating that the $\bar{K}N$ interaction is repulsive,
contradicting $\bar{K}N$ scattering experiments.
To improve the poor signal-to-noise ratio of these experiments,
experiments were conducted at KEK PS using gaseous hydrogen targets, and a negative energy shift was reported,
thus confirming that the $\bar{K}N$ interaction is attractive \cite{KEK_E228}.

Once the $\bar{K}N$ scattering experiments and characteristic $X$-ray measurements were found to be qualitatively consistent,
this led to further investigations into the $\bar{K}N$ interaction.
The scattering length from characteristic $X$-ray measurements was determined more precisely by DEAR \cite{Dear} and the SIDDHARTA Collaboration \cite{SHIDDARTA}.
The values of these experiments are also shown in Figure \ref{fig:KN_int}.
The SIDDHARTA data serve as a crucial constraint on the $\bar{K}N$ mass threshold,
playing a key role in constraining the $\bar{K}N$ scattering amplitudes discussed later.
