\input{intro/figs/L1405_pole}

Although the various experiments described above do not provide conclusive information on the poles of $\Lambda(1405)$,
they play an important role in theoretical studies.
Building on these results, theoretical studies based on the chiral unitary model have aimed to obtain more detailed $\bar{K}N$ scattering amplitudes while imposing chiral symmetry and unitarity conditions.

Y. Ikeda et al. \cite{Ikeda} and Z.-H. Geo et al. \cite{Geo} theoretically calculated the $\bar{K}N$ scattering amplitudes
by incorporating not only the results of $\bar{K}N$ scattering experiments but also the SIDDARTA experimental results as constraints,
including not only the leading order but also the next-to-leading (NLO) order in their analysis.
M. Mai et al. derived several solutions through a similar analysis and tested them against the results of the CLAS experiment \cite{Mai}.
However, since the CLAS experimental data require reaction-specific calculations for fitting,
they could not be directly incorporated into the fitting procedure.
Instead, they were used as a filter to evaluate the resulting solutions, leaving two viable candidates.

Since chiral unitary calculations are based on perturbative expansions at low momentum,
low-momentum $\bar{K}N$ scattering data have been primarily used.
However, due to experimental difficulties, the available low-momentum data are insufficient,
whereas medium- to high-momentum scattering data are more abundant.
Partial wave analysis is known as a method applicable to this energy region and has been extensively studied,
as described in Section \ref{sec:KN_interaction}.
It continues to evolve with the incorporation of new data \cite{KSU,KSU2}.
However, even with this approach, drawing conclusions at low momentum has been difficult due to the presence of $\Lambda(1405)$.
To overcome this challenge, the $\bar{K}N$ scattering amplitudes analyzed using the DCC model, a dynamic extension of partial wave analysis, were reported \cite{DCC1}.
The analysis produced two solutions for the scattering amplitudes, primarily due to the lack of data in the low-momentum region.
Although both scattering amplitudes exhibit two poles in the $S$-wave scattering below the $\bar{K}N$ mass threshold,
similar to the chiral unitary model, the parameters of these poles were very different.
The pole positions of $\Lambda(1405)$ based on the theoretical analysis presented in this chapter are summarized in Figure \ref{ref:L1405_pole}.
