\input{discussion/figs/obtained}

\section{Obtained spectra}
We obtained spectra of $d(K^-, n)"\pi^+\Sigma^-"$, $d(K^-, n)"\pi^-\Sigma^+"$ and $d(K^-, n)"\pi^-\Sigma^0"$.
We also obtained spectrum of $d(K^-, n)"n K^0$ as a sample of 1-step reaction.
These spectra is shown in Fig.\ref{fig:obtained}.
% The spectrum of $d(K^-, n)"n K^0"$ araise from the $\bar{K}N$ threshold, that guarantee about accuracy of the $d(K^-, n)$ missing mass.
In $d(K^-, n)"n K^0"$ reaction, the neutron identified by the missing mass is a spectator neutron,
the $d(K^-, n)"X"$ spectrum has the bump structure above the $\bar{K}N$ threshold whose peak around about $1.45 GeV/$c.
Such a kind reaction is called quasi-elastic scattering and qusi-elastic peak.
The 2-step reaction is considered dominant in spectra of $d(K^-, n)"\pi^{\mp}\Sigma^{\pm}"$ and $d(K^-, p)"\pi^- \Sigma^0"$, 
and the S-wave scattering is considered dominant as discribed in Sec.\ref{sec:kd_reaction}.
Actually, peaks of the $\Sigma(1385)$ and $\Lambda(1520)$ which is P-wave and D-wave scattering are not observed as Fig.\ref{fig:obtained}.

\dKPpimSz which is pure $I=1$ scattering in 2-step is strongly reflect shape of quasi-elastic scattering in 1-step shape due to smooth shape in 2-step caused from no structure.
On the other hands, \dKNpimpS which including $I=0,1$ and these interference term in 2-step is observed large contribution below the $\bar{K}N$ threshold,
that is considered as the $\Lambda(1405)$ contribution.
And, the difference between \pimSp and \pipSm represents the interference term of $I=0$ and $I=1$ which was clearly seen.
