\subsection{$d(K^-, n)$ scaling factor}
$d(K^-, n)"X"$ spectrum can be converted from counts to the differential cross section ($\frac{d^2\sigma}{d\Omega dm}$) excepting the acceptance of the the CDS that is depend on the reaction.
The parameters was used for the conversion were summarized in Table\ref{tab:KN_scale}.

First one is luminosity which was consist of number of target, number of irradiated kaon, DAQ live rate, trigger efficeincy.
The number of target was defined from length of fiducial volume ($10cm$) and target density which was evaluated from measured tempature.
The number of irradiated kaon was defined by correcting kaon number counted up by the scaler DAQ by ratio of true kaon in kaon trigger which was described in Sec\ref{sec:beam_line_ana}.
About DAQ live rate and trigger efficiency were discribed in Sec\ref{sec:trigger}.
The luminosity was evaluated run-by-run.
In the table, these items were represented value weighted by data statistics as typical value.

Next is about the CDS which was CDC efficiency discribed in Sec\ref{sec:CDC_eff}.
Accpectances of CDS were estimated and corrected by the Monte Carlo simulation data.
These evaluations were described in individual section for each reactions.

Last one is about the NC which was consists of acceptance and efficiency.
The efficiency of the NC was further decomposed to intrinsic one and overveto by the CVC and the BVC that was described in Sec\ref{sec:NC_eff}.
The acceptance of the NC was estimated from the NC position and the error was evaluated from difference of the first layer and the last layer of the NC.

\input{analysis/KN_scaling_table}

